---
title: "Assignment6QM"
output: html_document
---

```{r}
library(Benchmarking)
x <- matrix(c(150,400,320,520,350,320,0.2,0.7,1.2,2,1.2,.7),ncol = 2)
y <- matrix(c(140000,140000,420000,280000,190000,140000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(x) <- c("staff_hours","supplies")
colnames(y) <- c("reimbursed","privetly_paid")
x
y
```


```{r}
e1 <- dea(x,y,RTS = "crs") 
# provide the input and output 
peers(e1) 
# identify the peers
lambda(e1) 
# identify the relative weights given to the peers
dea.plot.isoquant(x,y,RTS="crs") 
# plot the results
summary(e1)
```

```{r}
e2 <- dea(x,y,RTS = "vrs") 
# provide the input and output 
peers(e2) 
# identify the peers
lambda(e2) 
# identify the relative weights given to the peers
dea.plot.isoquant(x,y,RTS="vrs") 
# plot the results
summary(e2)
```

```{r}
e3 <- dea(x,y,RTS = "irs") 
# provide the input and output 
peers(e3) 
# identify the peers
lambda(e3) 
# identify the relative weights given to the peers
dea.plot.isoquant(x,y,RTS="irs") 
# plot the results
summary(e3)
```

```{r}
e4 <- dea(x,y,RTS = "drs") 
# provide the input and output 
peers(e4) 
# identify the peers
lambda(e4) 
# identify the relative weights given to the peers
dea.plot.isoquant(x,y,RTS="drs") 
# plot the results
summary(e4)
```

```{r}
e5 <- dea(x,y,RTS="fdh") 
# provide the input and output 
peers(e5) 
# identify the peers
lambda(e5) 
# identify the relative weights given to the peers
dea.plot.isoquant(x,y,RTS="fdh") 
# plot the results
summary(e5)
```

```{r}
e6 <- dea(x,y,RTS="fdh+") 
# provide the input and output 
peers(e6) 
# identify the peers
lambda(e6) 
# identify the relative weights given to the peers

# plot the results
summary(e6)
```

##Compariative Analysis
As for the analysis, I will summarize the efficency results as a function of different DEA technology assumptions.


fdh: FDH technology and input orientated efficiency
Number of firms with efficiency==1 are 6 out of 6 
Mean efficiency: 1 
                
  Eff range      #   %
        E ==1    6 100



vrs: VRS technology and input orientated efficiency
Number of firms with efficiency==1 are 5 out of 6 
Mean efficiency: 0.983 
               
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     0  0
        E ==1    5 83



drs: DRS technology and input orientated efficiency
Number of firms with efficiency==1 are 4 out of 6 
Mean efficiency: 0.974 
                
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     1 17
        E ==1    4 67



crs: CRS technology and input orientated efficiency
Number of firms with efficiency==1 are 4 out of 6 
Mean efficiency: 0.974 
              
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     1 17
        E ==1    4 67



irs: IRS technology and input orientated efficiency
Number of firms with efficiency==1 are 5 out of 6 
Mean efficiency: 0.983 
               
  Eff range      #  %
  0.8<= E <0.9   1 17
  0.9<= E <1     0  0
        E ==1    5 83



frh: ADD technology and input orientated efficiency
Number of firms with efficiency==1 are 6 out of 6 
Mean efficiency: 1 
               
  Eff range      #   %
        E ==1    6 100


It was found that DMU(5) and DMU(6) were 97.75% and 86.75% efficent, respectively. The mean efficiency = 97.4%.

