---
title: "R Notebook"
output: html_notebook

---
```{r}
library(caret)
library(ISLR)
library(e1071) 

flight <- read.csv("FlightDelays.csv")
flight1 <- flight[,c(-3, -5, -6, -7 ,-9, -11, -12)] ## remove 3,5,6,7,9,11,12 column from dataset
head(flight)
str(flight1)
```


```{r}

flight$Flight.Status = as.factor(flight$Flight.Status) ##Change Flightstatus to factor
flight1$DAY_WEEK = as.factor(flight1$DAY_WEEK) ##Change Day_week to factor
flight1$CRS_DEP_TIME = as.factor(flight$CRS_DEP_TIME) ##Change CRS_DEP_TIME to factor
```

QS1) 
Divide the data into 60% training and 40% validation
```{r}
##Clean the data, and divide into training and Validation
set.seed(123)
Train_Index = createDataPartition(flight1$Flight.Status,p=0.6,list=FALSE)  ##divide the data into training and validation.
Train_Data = flight1[Train_Index,]
Validation_Data = flight1[-Train_Index,]


summary(Train_Data)
NROW(Train_Data)
head(Train_Data)
NROW(Validation_Data)
prop.table(table(flight1$Flight.Status)) * 100
prop.table(table(Train_Data$Flight.Status)) * 100
prop.table(table(Validation_Data$Flight.Status)) * 100



```

Qs2)
Run the Naive Bayes model to predict whether the flight is delayed or not. Use only categorical variables for the predictor variables. Note that Week and Time variables need to recoded as factors
```{r}
# Build a naïve Bayes classifier

nb_model <-naiveBayes(Flight.Status~CRS_DEP_TIME+CARRIER+DEST+ORIGIN+DAY_WEEK,data = Train_Data)
nb_model
```

QS3)
Output both a counts table and a proportion table outlining how many and what proportion of flights were delayed and ontime at each of the three airports
```{r}
nb_model <-naiveBayes(Flight.Status~ORIGIN,data = Train_Data)
nb_model
```


Qs4)
Output the confusion matrix 
```{r}
##Now, use the model on the Validation set
Predicted_Valid_labels <-predict(nb_model,Validation_Data)

library("gmodels")

# Show the confusion matrix of the classifier
CrossTable(x=Validation_Data$Flight.Status,y=Predicted_Valid_labels, prop.chisq = FALSE)
##Our results indicate that we misclassified a total of 189 cases. 138 as False Positives, and 51 as False Negatives.

```


```{r}
##lets output the raw prediction probabilities rather than the predicted class. To do that, we use the raw option in the model.
nb_model <- naiveBayes(Flight.Status~CRS_DEP_TIME+CARRIER+DEST+ORIGIN+DAY_WEEK,data = Train_Data)


#Make predictions and return probability of each class
Predicted_validation_labels <-predict(nb_model,Validation_Data, type = "raw")

#show the first few values 
head(Predicted_validation_labels)
```

Qs 4 )
Output ROC for the validation data
```{r}
## We can now output the ROC curves.
library(pROC)

#Passing the second column of the predicted probabilities 
#That column contains the probability associate to 'ontime’
roc(Validation_Data$Flight.Status, Predicted_validation_labels[,2])
```


##Plot the ROC
```{r}
plot.roc(Validation_Data$Flight.Status,Predicted_validation_labels[,2])

```








